# high order function
a function takes functions as args,
or return functions;

apply  family of functions

```{r}

sapply() # simply apply output
vapply() # coerce output and error out if failed
lapply() # map over lists
tapply() # work on ragged-table, "jagged" row lengths

```

remind me the similar functions in Python pandas;

```{Python}

apply()    # on colomn or row
map()      # series
applymap() # dataframe

```

# currying

point-free programming or tacit programming

```{r}

f <- function(x, y) x + y

f <- function(x) {
    return(
        function(y) {
            x + y
        }
    )
}

# or

h <- function(f) function(x) function(y) f(x, y)

h(`+`)(2)(3)

```

# Thunks and Trampolines

thunk      : https://en.wikipedia.org/wiki/Thunk
trampoline : https://en.wikipedia.org/wiki/Trampoline_(computing)

### box 1{.box-4 .bg-red}

Historical note:
There are a couple of onomatopoeic myths circulating about the origin of this term.
The most common is that it is the sound made by data hitting the stack;
another holds that the sound is that of the data hitting an accumulator.
Yet another holds that it is the sound of the expression being unfrozen at argument-evaluation time.
In fact, according to the inventors,
it was coined after they realized (in the wee hours after hours of discussion) that the type of an argument in Algol-60 could be figured out in advance with a little compile-time thought,
simplifying the evaluation machinery.

In other words, it had “already been thought of”; thus it was christened a thunk,
which is “the past tense of 'think' at two in the morning”.

```{r}

make_thunk <- function(f, ...) {
  force(f)
  params <- list(...)
  function() do.call(f, params)
}

trampoline <- function(thunk) {
  while(is.function(thunk)) thunk <- thunk()
  thunk
}

thunk_fact <- function(n, continuation=identity) {
  if(n==1) {
    continuation(1)
  } else {
    new_continuation <- function(result) {
      make_thunk(continuation, n * result)
    }
    make_thunk(thunk_fact, n - 1, new_continuation)
  }
}

thunk_fact(1)
thunk_fact(2)()()
thunk_fact(3)()()()()

trampoline(thunk_fact(100))

```
