# LEGB

## global environment

```{r}

x <-2; y <- 2

quote(x + y)

eval(x + y)

eval(quote(x + y))

```

## new global environment
```{r}
env <- new.env()
env$x <- 4
```

### shortcut
```{r}
env <- list2env(list(x=4))
```

### unquote
```{r}
eval(x + y, env)
```

### quoted
```{r}
eval(quote(x + y), env)
```

# R compiler, environment chain

when u call a function in R, you first create an environment for that function
that environment is where its parameters will be stored,
and any local variables the function assigns to it will go there as well;

that environment is linked to another environment

["variable -> value]

the concept is really close to class environment in Python;

```{r}
f <- function(x) 2 * x
x <- 4
f(2)

```

["f -> function(x) 2 * x]
["f -> function(x) 2 * x, "x -> 4]
[] -> ["f -> function(x) 2 * x, "x -> 4]

before any of the code in the function starts executing,
the function parameters are put into this environment,
so when we start executing the code in function f,
the environment chain looks like this:

["x -> 2] -> ["f -> function(x) 2 * x, "x -> 4]

# <<- operator
search through the environment chain,
the same way R does to figure out what expr should evaluate to
and to update the environment where it finds the variable.

```{r}

counter <- function() {
    x <- 0
    return(
        function() {
            x <<- 1
            x
        }
    )
}

counter() # 1
counter() # 2

```

remind me the `koenig lookup` in C++

